---
title       : Developing Data Products Course Project
subtitle    : Area Calculator
author      : Andrew Hwang
job         : 
framework   : io2012        # {io2012, html5slides, shower, dzslides, ...}
highlighter : highlight.js  # {highlight.js, prettify, highlight}
hitheme     : tomorrow      # 
widgets     : []            # {mathjax, quiz, bootstrap}
mode        : selfcontained # {standalone, draft}
knit        : slidify::knit2slides
---

## Area Calculator

The Shiny application created for the course project calculates the area of a user-chosen shape and user-specified dimensions.

The application dynamically changes as the user changes the input of the various fields.

This application allows user to quickly calculate the area of a square, rectangle, triangle, circle, or parallelogram.

--- .class #id 

## How to Use the Calculator

Upon opening the application, the user will see that the default values are that the shape is square and the length is 0, thus giving an area of 0.

To change the shape, the user must click on the drop-down menu and choose the desired shape. The possible choices are square, rectangle, triangle, circle, and parallelogram.

Upon making a choice of shape, take note that the choice is automatically reflected on the right panel. Furthermore, the input boxes below the drop-down menu may have also changed depending on the selection.

--- .class #id

## How to Use the Calculator (cont.)

Next, enter the desired value(s) for the shape. If the shape chosen is a circle or square, there is only one value to enter (radius and length respectively). The other shapes require two values (length and width).

Upon entering values, the area is automatically calculated and displayed on the right panel, just below the message displaying what shape the user chose.

To do another calculation, simply choose the desired shape and input the desired values again. There is no need to restart the application.

--- .class #id

## Examples

Here are some example inputs and their expected outputs.

If we want to find the area of a circle with radius 2.5, the area is calculated as follows:
```{r}
radius <- 2.5
pi*radius^2
```

A triangle with height 7 and width 4 has area:
```{r}
length <- 7; width <- 4
(length*width)/2
```